An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies

### 2017-05-08 main.tex
Modify ranking to consider mean not median.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{./img/median_rank_vs_population_size_invade.pdf}
    \caption{Ranks of all strategies according to \(x_1\) for different
    population sizes}
    \label{fig:ranks_v_size_invade}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{./img/median_rank_vs_population_size_resist.pdf}
    \caption{Ranks of all strategies according to \(x_{N-1}\) for different
    population sizes}
    \label{fig:ranks_v_size_resist}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{./img/median_rank_vs_population_size_coexist.pdf}
    \caption{Ranks of all strategies according to \(x_{N/2}\) for different
    population sizes}
    \label{fig:ranks_v_size_coexist}
\end{figure}

>>>>

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_invade.pdf}
    \caption{Ranks of all strategies according to \(x_1\) for different
    population sizes}
    \label{fig:ranks_v_size_invade}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_resist.pdf}
    \caption{Ranks of all strategies according to \(x_{N-1}\) for different
    population sizes}
    \label{fig:ranks_v_size_resist}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_coexist.pdf}
    \caption{Ranks of all strategies according to \(x_{N/2}\) for different
    population sizes}
    \label{fig:ranks_v_size_coexist}
\end{figure}
